% 350-word limit
\begin{abstract}
The extraction of neuron morphology from microscopy imaging data is an
invaluable method for understanding neuron characteristics. However, due to the
cost in time and effort, manual neuron reconstruction is not feasible
for large-scale analysis of neuron datasets. Furthermore, the issues of noisy
and low-contrast data, multiple scales across datasets, and inter-operator
variability of neuron tracing between experts make the analysis of the neuron
morphology a challenging task for both humans and computers.

Over the past decade, multiple methods and systems for neuron morphology
extraction from 3D microscopy images have been proposed; however, directly
comparing and collating the results of these methods has been difficult due to
the complexity involved in reimplementing all the stages of the reconstruction
pipeline. Recent developments have made it possible to collaboratively share
both neuron imaging data and code between organisations. This thesis presents
the design and implementation of a complete system for neuron morphology
extraction that can be integrated into graphical tools so neuroscience
researchers can analyse their own neuron data and compare the output against
both manual and automated tracings.

The thesis describes a system for the segmentation, registration, and
centreline extraction of 3D neuron data from various kinds of neurons.
The software is integrated into a popular toolkit for biomedical
image analysis for ease-of-use and visualisation. The system includes an
extensive test suite of for both the individual components (unit testing) as
well as across the whole system (integration tests).
\end{abstract}
        \centerline{\vrule width 1.5in height 0.4pt}
\noindent\textbf{Keywords}: neurons, cell morphology, biomedical image analysis, software engineering
