\documentclass[12pt]{article}
\input{preamble/helper.tex}
\input{00_front-matter/notation.tex}
\input{preamble/draftwatermark.tex}

\title{Algorithm}
\author{Zakariyya Mughal}
\date{2015-12-12}

\begin{document}
\maketitle
\tableofcontents

For the following, all indices are 0-based in order to match the
indexing found in the \gls{orionc} code and reduce the need for
subtracting one when calculating using indices.

\section{Segmentation}

\subsection{Input}

\newcommand{\foobar}[1]{\bm{#1}}

\begin{description}
	\item[\(\InputVolumeName{}\)] is the input volume of dimensions
		\(\InputVolumeDimensions{}\) which contains the intensity values taken
		from the microscope modality.
	\item[\(\RadiiScalesName{}\)] is a \Dim{\RadiiScalesName}-tuple where each element
		\(\RadiiScalesElem \in \RadiiScalesName\)
		represents the radius of the neurite to segment.
	\item[\(\LaplacianFilterApproxDegree{}\)] is the degree of the
		exponential Taylor series used to calculate the approximation
		to the Laplacian filter. This is set to \(\num{60}\) based on Paul's
		experiments.
	\item[\(\LaplacianFilterScaleFactor{}\)] is a factor that
		is used to find the scale of the Laplacian filter
		filter for which a tubular structure with a radius
		\(\RadiiScalesElem \in \RadiiScalesName\)
		gives a maximal response. This is fixed for a
		given value of \(\LaplacianFilterApproxDegree\).
\end{description}

\subsection{Extract features}

\subsubsection{Laplacian scale parameter}

\(\LaplacianScalesName\) is a \Dim{\RadiiScalesName}-tuple such that
\begin{equation*}
	\LaplacianScalesName \ni \LaplacianScalesElem{} = \frac{\RadiiScalesElem{}}{\LaplacianFilterScaleFactor}
\end{equation*}

\todo{explain that \(\LaplacianFilterScaleFactor = \num{0.66}\) was chosen by using linear regression and fixing
\(\LaplacianFilterApproxDegree{} = \num{60}\).}

\subsubsection{Hessian scale parameter}

\(\HessianScalesName\) is a \Dim{\RadiiScalesName}-tuple where each element
\begin{equation*}
	\HessianScalesName \ni \HessianScalesElem{} = \RadiiScalesElem{}
\end{equation*}
that is, the radius at which to segment.

\subsubsection{Laplacian filter (HDAF)}

\(\LaplacianOutputVolumeName\) is a \Dim{\RadiiScalesName}-tuple
where each element \(\LaplacianOutputVolumeElem \in \LaplacianOutputVolumeName\)
is a \Dim{\InputVolumeName}-dimensional volume
that contains the filter response for the corresponding Laplacian scale \(\LaplacianScalesElem\).

\subsubsection{Hessian filter}


Hessian filter is defined for a function \(\FuncTo{f}{\Sreal^{n}}{\Sreal}\)
as
\begin{equation*}
	H(f)_{i,j}(\vect{x}) = \frac{\partial{}^{2} f(\vect{x})}{\partial{}x_{i}\partial{}x_{j}}
\end{equation*}
for a point \(\vect{x} = (x_0, x_1, x_2, \dotsc, x_{n-1}) \in \Sreal^{n}\)

For a 3D volume \(\tens{V}\), we compute the Hessian as
\begin{equation*}
	H(\tens{V})_{i,j}(\vect{x}) = \frac{\partial{}^{2} \tens{V}(\vect{x})}{\partial{}x_{i}\partial{}x_{j}}
\end{equation*}
where \(\vect{x} = (x_{0}, x_{1}, x_{2})\) is a point in the 3D
coordinate system of \(\tens{V}\).

\todo{explain how a Gaussian 2nd derivative filter is used to smooth piecewise noise from discrete volume}

\(\EigFirstName\), \(\EigSecondName\), and \(\EigThirdName\) are
are each \Dim{\RadiiScalesName}-tuples where the elements
\begin{equation*}
\begin{aligned}
	\EigFirstElem  &\in \EigFirstName  \\
	\EigSecondElem &\in \EigSecondName \\
	\EigThirdElem  &\in \EigThirdName  \\
\end{aligned}
\end{equation*}
are each \Dim{\InputVolumeName}-dimensional volumes
containing the first, second, and third eigenvalues respectively of \(H(\InputVolumeName)\)
for scale \(\HessianScalesElem\).
Each 3-tuple of eigenvalues is sorted so that
\(\abs{\EigFirstElem\InputVolumeElemIndices}
\le \abs{\EigSecondElem\InputVolumeElemIndices}
\le \abs{\EigThirdElem\InputVolumeElemIndices}\)
(i.e., the eigenvalues are sorted in ascending
order).

\subsection{Background training set}

The training set for the the background class is made up of pixels that are
either on the background

\subsubsection{Maximal Laplacian filter response}

\begin{equation*}
\MaxResponseLaplacianElemIndices = \argmax_{s} \(\LaplacianOutputVolumeElemIndices\)
\end{equation*}
where \(\MaxResponseLaplacianName\) is a volume of dimension
\(\Dim{\InputVolumeName}\) where each element is an index such that
all elements satisfy
\(0 \le \MaxResponseLaplacianElemIndices < \Dim{\RadiiScalesName}\)


\subsubsection{Feature vector}


\begin{equation*}
\FeaturesElemIndices = \Set{
\left(
	\EigSecondElemIndices,
	\EigThirdElemIndices
\right)
|
s = R_{\mathrm{max}}^{L}\InputVolumeIndices
}
\end{equation*}
where \(\FeaturesName\) is a volume of dimensions \(\Dim{\InputVolumeName}\) with
elements that are each tuples of length two, that is, the number
of eigenvalues used as features.

\subsection{Discriminant function}

\subsubsection{Input}

\begin{description}
	\item[\(\FeaturesName\)] is a volume that contains the feature vector for each
		voxel in the volume.
	\item[\(\HistogramBinCount\)] is a scalar number of bins.
\end{description}

\subsubsection{Bin bounds and edges}

The 2D histogram minima and maxima are computed for each feature
\begin{equation*}
	\HistogramMinElem = \min \Set{ f_{\FeatureIndex} | f_{\FeatureIndex} \in ( f_0, f_1 ) = f \in \FeaturesName }
\end{equation*}
\begin{equation*}
	\HistogramMaxElem = \max \Set{ f_{\FeatureIndex} | f_{\FeatureIndex} \in ( f_0, f_1 ) = f \in \FeaturesName }
\end{equation*}

Bin edges are computed for each \(\mnth{{\FeatureIndex}}\) feature
\begin{equation*}
	b_{\FeatureIndex}[w] =
		\HistogramMinElem +
		\frac{ \HistogramMaxElem  - \HistogramMinElem  }
		     { \HistogramBinCount } \, w
\end{equation*}
where \(w\) is the index of the leading edge to the
\(\mnth{w}\) bin and \( 0 \le w \le  \HistogramBinCount \).

\subsubsection{Histogram accumulation}

\begin{equation*}
	H[x,y] =  \Dim{ \BinFunc(\FeaturesName, x, y) }
\end{equation*}
where \(H[x,y]\) is a \(\HistogramBinCount \times \HistogramBinCount\) matrix and
where \(\operatorname{Bin}(\FeaturesName, x, y)\) is the set of all tuples
\((f_0, f_1) \in \FeaturesName\) such that
\begin{enumerate}
	\item \(b_0[x] \le f_0 < b_0[x+1]\) and
	\item \(b_1[y] \le f_1 < b_1[y+1]\).
\end{enumerate}



\section{Tracing}

\end{document}
