\documentclass[12pt]{article}
\input{preamble/helper.tex}
\bibinput{thesis}
\bibliography{thesis}

\title{Annotated bibliography}
\author{Zakariyya Mughal}
\date{2015-12-12}
\begin{document}
\singlespacing
\maketitle
\tableofcontents

% TODO take these and repurpose for 01_introduction/introduction.tex
% literature review

\section{Datasets}

\begin{enumerate}[label={}]
		\enumdescitem{\printarticle{Duke-Southampton-archive:Cannon:1998}}
			This paper describes a dataset of neuron
			morphology that was developed as a
			collaboration between Duke University and
			Southampton University. This early dataset
			introduced the SWC format for representing
			neuronal arbors.

		\enumdescitem{\printarticle{Ascoli2007}}
			This paper describes the
			NeuroMorpho.Org project which collects
			neuronal morphology submitted from various
			laboratories. These submissions are used
			to perform statistical analysis in order
			to characterise different kinds of
			neurons. These data are taken from various
			cell types and different species. Each
			reconstruction has metadata that can be
			searched to narrow down to certain kinds
			of neuron sources.

		\enumdescitem{\printarticle{DIADEM-dataset:Brown:2011}}
			This paper describes the datasets from the
			DIADEM Challenge. Each dataset was
			obtained from different laboratories using
			different protocols for data acquisition.
\end{enumerate}

\section{History}

\begin{enumerate}[label={}]
	\enumdescitem{\printarticle{DIADEM&Beyond:Liu:2011}}
		This editorial paper covers details of the DIADEM
		Challenge and summarises the results of the
		algorithms. It notes that many of the algorithms
		require human intervention to achieve a high level
		of accuracy against the gold standard tracings. It
		also notes that while many algorithms worked on
		multiple datasets, none of the algorithms were
		able to generalise to \emph{all} the datasets.
		It also describes several directions for future
		research:
		\begin{enumerate}[label={}]
			\enumdescitem{Time-lapse data}
				Moving from 3D volume data to 4D
				image sequences.
			\enumdescitem{Subcellular structures}
				Using markers to identify sites on the
				neuron itself that can be identified.
			\enumdescitem{Dense trees} Working with
				data that contains dense neuronal arbors
				as opposed to sparse neuronal cells that
				were used in many of the DIADEM datasets.
			\enumdescitem{Long-distance dendritic projections}
				Expand the dataset to include data
				that has longer neuronal
				projections that are common in
				dendrites.
			\enumdescitem{Electron microscopy}
				The DIADEM datasets all came from
				optical microscopy.
				Neuroscientists also make heavy
				use of EM data and this data is
				also useful for studying neuronal
				structures.
			\enumdescitem{Moving to neural circuits and the connectome}
				The DIADEM datasets only have
				single neurons, but
				neuroscientists eventually want to
				move on to imaging multiple
				neurons to see how the structure
				of connections is important for
				signaling.
		\end{enumerate}

	\enumdescitem{\printarticle{NeuroMorphTrends:Halavi:2012}}
		This review article provides a literature review
		of the various techniques used for neuron tracing
		using computers. This includes the early history
		from the late 1960s onwards towards the DIADEM
		Challenge. In particular, the paper provides an
		overview of the brain regions and cell types that
		are studied most often and the imaging modalities
		that are used by neuromorphologists. This data is
		obtained through literature mining of 902
		publications. In addition, the authors attempted
		to obtain the data from the papers that they cover
		in their literature mining survey and the results
		of this are available on NeuroMorpho.Org.

	\enumdescitem{\printarticle{NeuroTracePerspect:Meijering:2010}}
		This review article describes the difficulties faced when
		trying to acquire neuron morphology data and the
		various computational tasks that must be
		performed in order to perform digital
		reconstructions of the neuron data. It also
		contains a survey of various reconstruction tools
		that are available. This paper occurred before the
		completion of the DIADEM Challenge, so it does not
		cover later advances in neuron tracing.
\end{enumerate}

\section{Methods}

\begin{enumerate}[label={}]
		\enumdescitem{\printarticle{Bauer2010}}
			This paper presents a method for
			automatic segmentation of 3D volumes of blood
			vessels especially where the vessel tree
			contains many overlapping structures. This
			is achieved by first extracting the
			tubular shapes using a Hessian filter. The
			results of the Hessian filter are then
			further processed by using a medialness filter
			to suppress false data (such as tumors or
			overlapping structures) that might occur at
			the boundaries of the vessel. Once the
			tubular structures are detected, the
			centreline is extracted by traversing the
			medialness response along the path with
			maximal value.

			The centreline and boundary provides structural
			information that can be used to construct
			model of the vessel structure that takes
			into account properties of blood flow
			(vessel radius, branching angle). This
			structural information is then used as
			a shape prior for assigning each tube to a
			tree in order to handle multiple
			trees.
		\enumdescitem{\printarticle{MICCAI-anisotropic-path-searching-Xie2010}
		and \printarticle{MIA-anisotropic-path-searching-Xie2011}}
			These papers cover a method for tracing
			based on choosing seed points that
			represent the underlying neuronal
			structure and then connecting these seeds
			to produce a neuron tree. The seeding is
			initiated by applying a windowing cube on
			the volume in order to detect seed
			candidates at the local maxima. These
			seeds candidates are pruned to simplify
			tracing. Then a cost function is
			introduced in order to a find a path
			between the seed points. This cost
			function incorporates a smoothness term
			which constrains new edges between seed
			points so that large changes in
			orientation are avoided. Finally, these
			local edges are used to construct a
			global tree by using the
			minimal-spanning-tree (MST) algorithm.

		\enumdescitem{\printarticle{Jeong2015}}
			This paper presents a method that learns
			to correspond line segments with
			curvilinear structures. However, this does
			not cover reconstruction of 3D data.

		\enumdescitem{\printarticle{Luo2015}}
			This paper presents a method for neuron
			reconstruction that is based on an
			open-curve snake model. This method
			start by a seed detection step that is
			based on what is known as a Sliding Volume
			Filter which selects a spherical region
			around each voxel in order to calculate
			the orientation of the gradient vectors
			within that region relative to center of
			the spherical region. By calculating the
			filter response as the cosine of the
			orientation, regions with a high response
			have more voxels where the gradient is
			oriented towards the center which
			indicates a tubular region. This filter
			response is used for initial seed point
			selection. These seed points are further
			pruned by using the eigenvalues of the
			Hessian of the volume to choose points
			that lie along the centerline of the
			tubular structure. The intensity of the
			voxels at the seed points is recalculated to
			create an SVF-enhanced image which is then
			used by an open-curve snake model for
			neuron tracing. This model creates a
			deformable model that is used to add edges
			to a curve that extends along the
			direction of the eigenvalue of the Hessian
			calculated earlier.

		\enumdescitem{\printarticle{De2015}}
			This paper only handles 2D images.

		\enumdescitem{\printarticle{Gulyanon2015}}
			This paper uses a joint probability model
			to both optimize voxel labels (foreground,
			background) and open-curve snake model
			configurations. This probability model
			uses the Frangi vessellness features as a
			data prior. A Discriminative Random
			Field is used to determine initial labels
			for the voxel classifications and voxels
			with a high confidence are used as the 
			initial seed points of 3D snake configuration.
			This inference is performed on subvolumes
			so that the probability model only uses
			the local intensity distribution.

		\enumdescitem{\printarticle{Jimenez2013} and
		\printarticle{Hernandez-Herrera2013} and \printarticle{Hernandez-Herrera2014} and \printarticle{ORION_Santamaria-Pang2015}}
			In \autocite{Jimenez2013}, a method that
			first uses low-pass,
			high-pass, and Laplacian filter responses
			are used as features
			to train an SVM to classify voxels as
			being background or foreground. This is
			used to binarize the neuron data so that
			only a subset of the volume needs to be
			analysed for seed selection. Seed
			selection is performed by applying a
			distance transform to the binary volume
			and then only keeping voxels that have a
			greater distances than the average
			distance in the 26-neighborhood of that
			voxel. Tracing between these seed points
			is then done with a variation of
			Dijkstra's algorithm that adds weights
			based on the distance transform
			and on the orientation between each successive
			edge. These constraints keep the centerline path
			from deviating from the center of the
			tubular structure and from having sharp
			changes in direction.

			In \autocite{Hernandez-Herrera2013}, a
			general model of the frequency-domain
			properties involved in neuron data
			acquisition is described and used to
			generate synthetic data from the DIADEM
			tracing dataset.

			\Autocite{Hernandez-Herrera2014} describes
			a segmentation method based on one-class
			classification. This segmentation method
			uses the Laplacian filter response in
			order to create a training set of
			background voxels. Two representative
			eigenvalues of the Hessian filter are then
			used to create a discriminant function
			based on the distribution of these
			eigenvalues.

		%\enumdescitem{\printarticle{Basu2013} and \printarticle{Basu2014}}
		%\enumdescitem{\printarticle{Czarnecki2012}}
		%\enumdescitem{\printarticle{Lee2012}}
		%\enumdescitem{\printarticle{Ming2013}}
		%\enumdescitem{\printarticle{Mukherjee2013} and \printarticle{Mukherjee2014}}
		%\enumdescitem{\printarticle{Xiao2013}}
\end{enumerate}


\section{Metrics}

\begin{enumerate}[label={}]
		\enumdescitem{\printarticle{DIADEM-metric-Gillette2011}
		and \printarticle{Gillette2015}}
			This paper describes the metric used to
			compare the automated neuron tracing
			output against the DIADEM ground truth
			tracings. This method works on the SWC
			format which provides both spatial
			location and radius for each point in the
			neuron tree. The method of registering the
			test tracing to the gold standard tracing
			starts by choosing an unregistered gold
			standard bifurcation node. To check that
			there is a matching node in the test
			tracing, the method looks for a test node
			that is in within a cylindrical region
			around the same spatial location as the
			gold standard node in order to find a
			match. The matching continues along both
			the parent and any children of the gold
			standard node. In order to determine that
			a gold standard node and test node are
			sufficiently close, a path length error is
			calculated by taking the path length
			between a nodes in the test tracing
			divided by the corresponding path length
			in the gold standard tracing. As long as
			this path length error is within
			acceptable bounds, the path is considered
			a match. Finally, if there are any gold
			standard nodes that have not been
			registered, the algorithm tries to
			determine if any existing path that passes
			through that node in order to determine a
			match.

		\enumdescitem{\printarticle{Mayerich2011} and \printarticle{Mayerich2012}}
			This paper describes a method for
			measuring the similarity between two
			tracings by using a Gaussian-weighted distance
			field between a given point in one tree
			and the closest point in the other
			tree. This allows for small deviations
			between the two trees without excessive
			penalization. This similarity metric is
			then applied to every in one tree in order
			to determine a graph coloring that assigns
			each node in one tree to a corresponding
			node in the other tree.

		\enumdescitem{\printarticle{btmorph-Torben-Nielsen2014}}
			This paper describes the implementation of
			a library for measuring various
			neuromorphological measures of a single.
			It does not directly compare multiple
			trees.

		\enumdescitem{\printarticle{Costa2014}}
			This paper proposes a similarity metric by
			defining a log-likelihood scoring matrix
			based on whether or not neurons are of the
			same type. The application for this is not
			to compare two trees directly, but to
			cluster and search large databases of
			neuromorphology data.
\end{enumerate}

\end{document}
