\begin{acknowledgements}
	Firstly, I am grateful for working with for the guidance and mentorship
	of my advisor Dr.~Ioannis A.\ Kakadiaris --- in both research and personal
	matters. Dr.~Kakadiaris kept me on track and made sure that I had the
	resources to keep organized. His many suggestions for improving my
	work were valuable and those lessons will stay with me.

	In addition, I would like to thank my committee, Prof.~Shishir Shah and
	Prof.~Emanuel Papadakis for asking interesting questions and pushing me to
	learn and try new ideas both inside and outside the classroom.

	I would like to also thank Prof.~Demetrio Labate, Prof.~Emanuel Papadakis,
	Pankaj Singh, Burcin Ozcan, Pooran Negi, and Paul Hernandez-Herrera for
	enlightening discussions during our neuroscience research meetings and
	the image analysis seminars in the Department of Mathematics.

	To the members of the Computational Biomedicine Lab over the years
	of my undergraduate and graduate studies
	%: \begin{enumerate*}[label={}]
		%\item Abraham Baez,
		%\item Ali Memariani,
		%\item Dr.~Bassam Almogahed,
		%\item Dr.~Boris Efraty,
		%\item Boris Penaloza,
		%\item Dr.~Chaohui Wang,
		%\item Dr.~Christophoros Nikou,
		%\item Chrysanthi Chaleva Ntina,
		%\item Danil Safin,
		%\item Dat Chu,
		%\item Dr.~David Jim{\'{e}}nez,
		%\item Dr.~Deepak Roy Chittajallu,
		%\item Eleni Sgouritsa,
		%\item Eleni Zacharia,
		%\item Dr.~Emil Bilgazyev,
		%\item Dr.~Georgios Evangelopoulos,
		%\item Georgios Giannoulis,
		%\item Jesus-Omar Ocegueda-Gonzalez,
		%\item Le Anh Vu Ha,
		%\item Lingfeng Zhang,
		%\item Manuel Meyer,
		%\item Mengjun Leng,
		%\item Michael Fang,
		%\item Mohammed Islam,
		%\item Nikolaos Mitsakos,
		%\item Nikolaos Sarafianos,
		%\item Olga Carolina Avila Montes,
		%\item Oman Maga{\~{n}}a,
		%\item Panagiotis Moutafis,
		%\item Dr.~Paul Hernandez-Herrera,
		%\item Pengfei Dou,
		%\item Ricky Gentry,
		%\item Dr.~Sanat Upadhyay,
		%\item Siyang Wang,
		%\item Stanislav Yotov,
		%\item Dr.~Uday Kurkure
		%\item Vincent Christlein,
		%\item Xiang Xu,
		%\item Dr.~Yen Le Hai, and
		%\item Yuhang Wu
	\end{enumerate*}
	---
	I learned a lot from our conversations which sparked ideas for further
	research and new ways of approaching computer science and software engineering.
	Being able to learn from the diversity of projects in the lab was a
	quite enjoyable experience.

	I would like to acknowledge my family for their patience during the
	many hours that I would dissappear to work at the lab. I could not have
	completed my thesis without their help and encouragement.
\end{acknowledgements}
